---
title: "P8105 HW1"
author: "Maya Krishnamoorthy"
date: "2024-09-17"
output: github_document
---

## Problem 1

``` {r setup, echo=FALSE, message=FALSE}
library(tidyverse)
```

*Load the `penguins` dataset:*

``` {r}
data("penguins", package = "palmerpenguins")
```

``` {r, message=FALSE}
nrow_penguins = nrow(penguins)
ncol_penguins = ncol(penguins)
flipper_length_mm_mean = mean(pull(penguins, flipper_length_mm), na.rm=TRUE)

```

The data in this dataset holds information about penguins. It contains the following **variables**: species, bll length in mm, bill depth in mm, flipper length in mm, island, sex, and body mass in grams. The `penguins` dataset contains **`r nrow(penguins)` rows** and **`r ncol(penguins)` columns**. The **mean flipper length** of penguins in this dataset is **`r flipper_length_mm_mean` mm**.

*Make a scatterplot of `flipper_length_mm` (y) vs `bill_Length_mm` (x). Color points using the `species` variable.*

``` {r, message=FALSE}
penguins_scatter = ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) +
  geom_point()

penguins_scatter
```

*Export the scatterplot to the project directory using `ggsave`.*

``` {r, message=FALSE}
ggsave("penguins_scatter.png", plot = penguins_scatter)
```

## Problem 2
*Create a dataframe.*

```{r}
# NOT YET COMPLETED
hw_df = tibble(
  sample = rnorm(10),
  sample_log = (sample > 0),
  char_vec = sample(c(letters), 10),
  factor_vec = factor(sample(c("Level1", "Level2", "Level3"), 10, replace=TRUE))
)
```

*Try taking the mean of each variable in the dataframe. What works and what doesn’t?*

```{r}

```



